---
title: "Homework Assignment 1"
author: "Wade Rogers"
date: "March 14, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment

1. Create a new Rmarkdown document
1. Select an FCS file of your choice (preferably of your own data)
1. Create a section entitled *"Background"*.
1. Provide a brief description of the data (_e.g._ what research question it aims to answer,
what species, which markers, etc.)
1. Start a new section entitled *"Code and Data"*
1. Create a function that
    a. Accepts as an argument the name of a file
    a. Reads the file into a <code>flowFrame</code>
    a. Compensates it using the SPILL matrix embedded in the FCS header
    a. Performs a biexponential transformation
    a. Returns the resulting compensated and transformed <code>flowFrame</code>
1. Create a script that
    a. Source's the above function 
    q. Calls the above function
    a. Prints the flowFrame (by just mentioning its name)
    a. plots any 4 bivariate projections that you choose, 
    in a 2 x 2 plot area, and sets reasonable margins.  Hint: 
    ```{r eval=FALSE}
    par(mfrow = c(2, 2), mar = c(4, 4, .1, .1))
    ```
    

Execute your code in a code chunk of your Rmarkdown document, with echo=true so that the
script code will be displayed.

Finally, Knit your document (Word if you have it on your computer, HTML or PDF 
if you do not), and email the resulting document to me (wade.rogers@spcytomics.com).

Please remember that I'll be away next week.  I will give feedback at the beginning 
of our next session on March 28.


